Digital Addiction

### 2024-02-15 paper/paper.qmd
add cross reference and label for figures

---
title: "Digital Addiction"
subtitle: "My subtitle if needed"
author: 
  - Kenneth Chan, Stephanie Xuan Zhao, Siyu Li
thanks: "Code and data are available at: <https://github.com/YO7O/digital_addiction.git>"
date: today
date-format: long
abstract: "."
format: pdf
number-sections: true
#bibliography: references.bib
---

>>>>

---
title: "Digital Addiction"
subtitle: "Analysis of How Usage of Social Media Impact Objective Well-Being And Political Opinion"
author: 
  - Kenneth Chan, Stephanie Xuan Zhao, Siyu Li
thanks: "Code and data are available at: <https://github.com/YO7O/digital_addiction.git>"
date: today
date-format: long
abstract: "."
format: pdf
number-sections: true
#bibliography: references.bib
---
